\subsection{Related Work}
The {\em Liquid Democracy Journal}\footnote{https://liquid-democracy-journal.org/} collects many valuable literature about the liquid democracy problem, which begins at 2014 and almost information about latest progress can be found there. Blum and Zuber\cite{blum2016liquid} give an overview liquid democracy, include the concepts, the history and problems. Recently, a few technical papers also are interested in liquid democracy. Anson et al. \cite{kahng2018liquid} analyze the problem that whether there exists a delegate voting that outperforms direct voting, for the situation where there are a correct candidate and an incorrect candidate. Brill and Talmon \cite{brill2018pairwise} study the case where a voter can delegate to several proxies and specify a partial order. They propose a way to overcome the complications of individual rational. Christoff and Grossi \cite{christoff2017binary} analyze liquid democracy within the theory of binary aggregation, and consider the issues of individual rational and delegate cycle. 

 Recently, a series of literature studies the implementation of on-chain voting system \cite{hanifatunnisa2017blockchain,hjalmarsson2018blockchain}, some of which also refer to liquid democracy but not consider the self-tally requirement. The introduction of self-tally can be found in \cite{kiayias2002self}, which states that the property of self-tally and perfect ballot secrecy can not be satisfied simultaneously. Thus in this paper the privacy is compromised in favor of realtime self-tallying. Yang et al.\cite{yang2018decentralized} introduce a self-tallying voting system by Ethereum smart contract, but do not consider the liquid democracy scenario. McCorry et al. \cite{mccorry2017smart} also implement a distributed and self-tally electronic voting scheme using the Ethernet blockchain, while the core is to maximize the protection of voter privacy. 

To the best of our knowledge, our paper is the first $O(\log n)$ algorithm solving the on-chain liquid democracy problem, while the algorithms in Google vote and liquid feedback work in following ways: Google vote's algorithm mainly bases on the work of Schulze's \cite{schulze2011new}, which is a $m^3$ method for electing a winner, where $m$ is the number of candidates. They also demonstrate that the system can implement liquid democracy on a social network in a scalable manner with a gradual learning curve. The basics of Liquid Feedback's algorithm comes from Harmonic Weight\footnote{https://en.wikipedia.org/wiki/Harmonic\_mean}, Proportional Runoff\footnote{http://www.magnetkern.de/prop-runoff/prop-runoff.html} and Schulze method, whose proposes are to determine the weights of candidates. Though both  algorithms can be applied to liquid democracy, the self-tallying requirement and gas fee limitation are not taken into consideration.